
\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{ABSTRACT}
The Hybrid Phishing Defense System represents a transformative step forward in cybersecurity, merging the predictive agility of Deep Learning with the immutable trust of Blockchain technology. Conventional anti-phishing solutions rely heavily on centralized, reactive blacklists that fail to detect "zero-day" attacks. This project addresses these vulnerabilities by introducing a proactive, dual-layer defense framework.

\vspace{10pt}

The system utilizes a Hybrid CNN-LSTM Deep Learning model that dynamically analyzes 89 lexical and structural features of URLs in real-time. This specialized architecture effectively captures both spatial character anomalies and sequential structural obfuscations common in sophisticated phishing links, achieving highly accurate detection without relying on outdated databases. 

\vspace{10pt}

To overcome the vulnerabilities of centralized threat databases—such as single points of failure and censorship—the system integrates directly with the Ethereum Sepolia testnet via Smart Contracts. When a URL is classified as a critical threat, it is immutably logged to the blockchain, creating a tamper-proof and decentralized global threat registry. The final implementation includes a lightweight browser extension and a centralized dashboard, providing a robust, transparent, and proactive security ecosystem.

\vspace{20pt}

\noindent\textit{{\textbf{Keywords:}}Phishing Detection, CNN-LSTM, Blockchain, Smart Contracts, Web3 Security, Deep Learning.}

\newpage
